\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking} % Options: casual, classic, banking, oldstyle, fancy
\moderncvcolor{burgundy}

\usepackage[utf8]{inputenc}
\usepackage[scale=0.75]{geometry}

% Personal Data
\name{Patrick}{Schimpl, MA. MSc.}
\title{Polymath | Chem | Anthro | CS | Futures}
\address{Philippovichgasse 2-4/2/16}{1190 Vienna}{Austria}
\phone[mobile]{+43~699~11909500}
\email{patrick.schimpl@univie.ac.at}
\social[github]{cosmopax}

\begin{document}
\makecvtitle

\section{Executive Profile}
Polymathic researcher and developer bridging the gap between wet-lab chemistry, social anthropology, and computational intelligence. Proven track record in academic teaching, startup founding, and high-level policy consultation (OECD).

\section{Select Experience}
\cventry{2025}{Expert Consultant}{OECD - HQ}{Paris}{}{Invited expert for the \textit{Multistakeholder consultation on Responsible Innovation and Anticipatory Governance of Emerging Biotechnologies}. Focusing on policy frameworks for synthetic biology and AI convergence.}

\cventry{2021--Present}{Lecturer \& Research Associate}{University of Vienna}{Vienna}{}{Institutes of Organic \& Theoretical Chemistry. Medicinal Neurochemistry, Lab Automation, and teaching.}

\cventry{2025--Present}{Supervisor}{BISC-E Competition}{Europe}{}{Supervising BOKU University team for Bio-based Innovation Student Challenge.}

\cventry{2024--Present}{Judge}{iGEM Competition}{Global}{}{Evaluation of synthetic biology projects worldwide.}

\section{Education}
\cventry{2023--2025}{MSc in Chemistry}{University of Vienna}{Highest Honors}{}{Focus: Drug Development, Bioinformatics, Automation.}
\cventry{2019--2023}{MA in Cultural \& Social Anthropology}{University of Vienna}{}{}{Focus: Futures Studies, AI Architectures.}

\section{Technical Skills}
\cvitem{Computational}{Python, ML, Agential Frameworks, Automation Scripting}
\cvitem{Laboratory}{Flow Chemistry, Metabolic Engineering, NMR, HPLC}
\cvitem{Languages}{German (Native), English (Fluent), Spanish/French (Advanced)}

\end{document}
